Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-11 paper.qmd
Updated Figure 17

error_df <- error_df |>
  mutate(type = case_when(
    row_wise_abs_error <= 2 ~ "error 0-2",
    row_wise_abs_error <= 4 ~ "error 2-4",
    row_wise_abs_error <= 6 ~ "error 4-6",
    row_wise_abs_error <= 8 ~ "error 6-8",
    row_wise_abs_error <= 10 ~ "error 8-10",
    .default = "error greter than 10"
  )) |>
  mutate(type = factor(type, levels = c(
    "error 0-2", "error 2-4", "error 4-6", "error 6-8", "error 8-10", 
    "error greter than 10")))

@@

highd_error_2d_mnist <- error_df |>
  ggplot(aes(x = tSNE1,
             y = tSNE2, 
             color = type, 
             group = ID)) +
  geom_point(alpha=0.5, 
             size = 0.1) +
  scale_colour_brewer(
    type = "qual",
    palette = 2
  ) + 
  theme(
      legend.position = "bottom",
      legend.text = element_text(size = 10),          # Increase legend text size
      legend.key.size = unit(1, "lines")              # Increase size of legend keys
  ) +
  guides(
      color = guide_legend(
          override.aes = list(size = 2.5, alpha = 1)      # Increase point size and opacity in legend
      )
  ) 
```

@@

```{r}
#| label: fig-model-error-mnist
#| fig-cap: "(a) The $10\\text{-}D$ model error for tSNE layout in $\\gD{}$ of the MNIST digit 1 dataset. Most low model errors are distributed along the big non-linear clutser, while most large model errors are concentrated along the small cluster. (b) There are certain images that exhibit large errors due to their deviation from the non-linear cluster, which makes them anomalies. The images associated with large model errors shows different patterns of digit 1."
#| fig-pos: H
#| out-height: 80%

>>>>

# error_df <- error_df |>
#   mutate(type = case_when(
#     row_wise_abs_error <= 2 ~ "error 0-2",
#     row_wise_abs_error <= 4 ~ "error 2-4",
#     row_wise_abs_error <= 6 ~ "error 4-6",
#     row_wise_abs_error <= 8 ~ "error 6-8",
#     row_wise_abs_error <= 10 ~ "error 8-10",
#     .default = "error greter than 10"
#   )) |>
#   mutate(type = factor(type, levels = c(
#     "error 0-2", "error 2-4", "error 4-6", "error 6-8", "error 8-10", 
#     "error greter than 10")))

@@

## To transform the data
## ggplot(data = error_df, aes(x=row_wise_abs_error)) + geom_density() ## right skewed

error_df <- error_df |>
  mutate(sqrt_row_wise_abs_error = sqrt(row_wise_abs_error))

highd_error_2d_mnist <- error_df |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.2) +
  scale_colour_continuous_sequential(palette = "Light Grays")
  # scale_colour_brewer(
  #   type = "seq",
  #   palette = 1
  # ) #+ 
  # theme(
  #     legend.position = "bottom",
  #     legend.text = element_text(size = 10),          # Increase legend text size
  #     legend.key.size = unit(1, "lines")              # Increase size of legend keys
  # ) +
  # guides(
  #     color = guide_legend(
  #         override.aes = list(size = 2.5, alpha = 1)      # Increase point size and opacity in legend
  #     )
  # ) 
```

@@

```{r}
#| label: fig-model-error-mnist
#| fig-cap: "(a) The $10\\text{-}D$ model error for tSNE layout in $\\gD{}$ of the MNIST digit 1 dataset. Most low model errors are distributed along the big non-linear clutser, while most large model errors are concentrated along the small cluster. (b) There are certain images that exhibit large errors due to their deviation from the non-linear cluster, which makes them anomalies. The images associated with large model errors shows different patterns of digit 1."
#| fig-pos: H
#| fig-width: 10
#| fig-height: 5
#| out-height: 80%
